Co-citations in context

### 2019-06-14 cocit_r.tex
minor edit

We conclude that the choice of background datasets is the source of a majority of differences we observed in the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create \textcolor{blue}{material differences.}

>>>>

We conclude that the choice of background datasets is the source of a majority of differences we observed in the categories demonstrating the highest hit rates, although our sampling approach, most notably sampling from a multiset so as to reflect the observed frequencies of individual citations as well as their associated journals and disciplines, can also create material differences.
